### 2018-07-31 pilot_manuscript.Rmd
added the example mlm write up and table

```{r load_packages, include = FALSE}
library("papaja") #R says this package doesn't exist in current version :/
library(MuMIn)
knitr::opts_chunk$set(cache = TRUE)
```
# Introduction
Talk about MFT, MFQ, MFD (primer on moral psychology?)

@@

```{r mlm-analyses, include = FALSE}
##Attempt at MLM
mlm_data = final[ , -c(3:28) ]
library(reshape)
long_mlm = melt(mlm_data,
                id = c("X", "Source"))
colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
long_mlm$lean = factor(long_mlm$Source,
                       levels = names(table(long_mlm$Source)),
                       labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
long_mlm$lean = gsub("1", "", long_mlm$lean)

##set up the analysis
library(nlme)

#####intercept only model####
##gls = generalized least squares
##ML = maximum likelihood
model1 = gls(percent ~ 1, #DV ~ IV (which is only the intercept; is y-average diff than 0?)
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit")
summary(model1)

@@

```{r model-table, results='asis', include=FALSE}
tableprint = matrix(NA, nrow = 10, ncol = 10)

##stuff you had before
##three models
table = matrix(NA, nrow = 5, ncol = 10)

##ARE ALL OF THESE COLUMNS NEEDED?? ALSO, ORDER?
colnames(table) = c("Model", "Degrees of Freedom", "AIC", "BIC", 
                    "Log Likelihood", "R2m", "R2c", "Test", "L Ratio", "p-value")

##stick in the information you need
table[1, ] = c("Model 1", 2, 43610.91, 
               43627.55, -21803.46, "", "",
               "", "", "")

table[2, ] = c("Model 2", 3, 43611.04, 
               43636.01, -21802.52, 0.000, 0.004,
               "Model 1 vs Model 2", 1.871644, 0.173)

table[3, ] = c("Model 3", 4, 43604.33, 
               43637.62, -21798.17, 0.0003, 0.0037,
               "Model 2 vs. Model 3", 8.703020, 0.0032)

table[4, ] = c("Model 3.1", 13, 37913.11, 
               38021.30, -18943.55, 0.17, 0.19,
               "Model 3 vs. Model 3.1", 5709.23, "< .001")

table[5, ] = c("Model 3.2", 22, 37904.00, 
              38087.09, -18930.00, 0.17, 0.19,
               "Model 3.1 vs. Model 3.2", 27.11, 0.001)

@@

To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data. MLM is a regression technique that allows one to control for the repeated measurement and nest structured of the data, which creates correlated error [@CITE_gelman]. First, an intercept only model was created using percent text overall as the dependent variable. Using the *nlme* library in *R* [@CITE_nlme], a model with the news source as the random intercept was analyzed to determine if it was necessary to control for correlated error. Table @\ref(tab:model-table) includes the model statistics for all models.

#stopped here to ask questions

Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e. "harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run. Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.

```{r mlm, eval=FALSE, include=FALSE}

####random intercept only model####
##note we switched to LME function
model2 = lme(percent ~ 1, 
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno) #sets random intercept for each participant
summary(model2) #note changed Value in output; also, 
#Random effects tells how much intercept varies among Pps
anova(model1, model2) #tests if necessary to nest; Yes, we need to do MLM
r.squaredGLMM(model2)
####predictor model####
model3 = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3)
anova(model1, model2, model3)
r.squaredGLMM(model3) #gives you two, report both

model3.1 = lme(percent ~ lean + moraltype, #now we want to switch the 1 for IV of interest
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3.1)
r.squaredGLMM(model3.1)
model3.2 = lme(percent ~ lean * moraltype, #now we want to switch the 1 for IV of interest
               data = long_mlm, 
               method = "ML", 
               na.action = "na.omit",
               random = ~1|partno)
summary(model3.2)
r.squaredGLMM(model3.2)
##model 3 on each moral foundation separately
#h_hi
model3h_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno)
summary(model3h_hi)
tapply(long_mlm[long_mlm$moraltype == "hperhi", ]$percent,
       long_mlm[long_mlm$moraltype == "hperhi", ]$lean, mean)
#h_lo
model3h_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "hperlo", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3h_lo)
tapply(long_mlm[long_mlm$moraltype == "hperlo", ]$percent,
       long_mlm[long_mlm$moraltype == "hperlo", ]$lean, mean)
#f_hi
model3f_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "fperhi", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3f_hi)
tapply(long_mlm[long_mlm$moraltype == "fperhi", ]$percent,
       long_mlm[long_mlm$moraltype == "fperhi", ]$lean, mean)
#f_lo
model3f_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "fperlo", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3f_lo)
tapply(long_mlm[long_mlm$moraltype == "fperlo", ]$percent,
       long_mlm[long_mlm$moraltype == "fperlo", ]$lean, mean)
#i_hi
model3i_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "iperhi", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3i_hi)
tapply(long_mlm[long_mlm$moraltype == "iperhi", ]$percent,
       long_mlm[long_mlm$moraltype == "iperhi", ]$lean, mean)
#i_lo
model3i_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "iperlo", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3i_lo)
tapply(long_mlm[long_mlm$moraltype == "iperlo", ]$percent,
       long_mlm[long_mlm$moraltype == "iperlo", ]$lean, mean)
#a_hi
model3a_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "aperhi", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3a_hi)
tapply(long_mlm[long_mlm$moraltype == "aperhi", ]$percent,
       long_mlm[long_mlm$moraltype == "aperhi", ]$lean, mean)
#a_lo
model3a_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "aperlo", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3a_lo)
tapply(long_mlm[long_mlm$moraltype == "aperlo", ]$percent,
       long_mlm[long_mlm$moraltype == "aperlo", ]$lean, mean)
#p_hi
model3p_hi = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "pperhi", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3p_hi)
tapply(long_mlm[long_mlm$moraltype == "pperhi", ]$percent,
       long_mlm[long_mlm$moraltype == "pperhi", ]$lean, mean)
#p_lo
model3p_lo = lme(percent ~ lean, #now we want to switch the 1 for IV of interest
                 data = long_mlm[long_mlm$moraltype == "pperlo", ], 
                 method = "ML", 
                 na.action = "na.omit",
                 random = ~1|partno)
summary(model3p_lo)
tapply(long_mlm[long_mlm$moraltype == "pperlo", ]$percent,
       long_mlm[long_mlm$moraltype == "pperlo", ]$lean, mean)

Any more screening/data prep here?

Political lean of the news organization was used to predict the percent of words matching the Moral Foundations Dictionary. According to an analysis of variance (ANOVA) between the intercept-only model (Model 1) and the random intercept-only model (Model 2, *R2m* = 0.00, *R2c* = 0.004), there were no statistically significant differences (*F* = *?*, *p* = 0.17). There was a significant difference between the random intercept-only model and the predictor model (Model 3, *R2m* = 0.0003, *R2c* = 0.0037), *F* = *?*, *p* = .003).  We found a significant difference between the two political leans (*b* = -0.018, *SE* = 0.006, *t*(3039) = -2.95, *p* = 0.003). Next, we added Moral Foundation Type as a predictor of percent to the third model (Model 3.1, *R2m* = 0.17, *R2c* = 0.19). The ANOVA revealed a significant difference between Models 3 and 3.1, *F* = *?*, *p* < .001)

#Significance for, like, all of the little moral types. Put in table?

Finally, we analyzed the interaction between political lean and Moral Foundation type as a predictor of percent (Model 3.2, *R2m* = 0.17, *R2c* = 0.19). Using ANOVA, we found a significant difference between Models 3.1 and 3.2, *F* = *?*, *p* = .001).

#Again, lots of stuff here. Needs to be reported? Put in table?

Comparisons between the models can be found in Table 1. 
# Discussion
How it turned out

>>>>

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)

knitr::opts_chunk$set(cache = TRUE)
```
# Introduction
Talk about MFT, MFQ, MFD (primer on moral psychology?)

@@

```{r mlm-analyses, echo=FALSE, warning=FALSE, include = FALSE}
##Attempt at MLM
mlm_data = final[ , -c(3:28) ]
long_mlm = melt(mlm_data,
                id = c("X", "Source"))
colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
long_mlm$lean = factor(long_mlm$Source,
                       levels = names(table(long_mlm$Source)),
                       labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
long_mlm$lean = gsub("1", "", long_mlm$lean)

#####intercept only model####
##gls = generalized least squares
##ML = maximum likelihood
model1 = gls(percent ~ 1, 
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit")
summary(model1)

####overall percent - random intercept by source####
model3 = lme(percent ~ 1,
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model3)
r.squaredGLMM(model3)

####separate models by type####
##MFD category ~ lean 
model4.1 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.1)
r.squaredGLMM(model4.1)

model4.2 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.2)
r.squaredGLMM(model4.2)

model4.3 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.3)
r.squaredGLMM(model4.3)

model4.4 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.4)
r.squaredGLMM(model4.4)

model4.5 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.5)
r.squaredGLMM(model4.5)

model4.6 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.6)
r.squaredGLMM(model4.6)

model4.7 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.7)
r.squaredGLMM(model4.7)

model4.8 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.8)
r.squaredGLMM(model4.8)

model4.9 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.9)
r.squaredGLMM(model4.9)

model4.10 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.10)
r.squaredGLMM(model4.10)

@@

```{r model-table, results='asis', echo=FALSE}
tableprint = matrix(NA, nrow = 12, ncol = 7)

colnames(tableprint) = c("Model", "AIC", "BIC", "$\\chi^2$", "$df$",
                         "$R^2_m", "$R^2_c")

#put in each model set information
#temp store model summary
temp = summary(model1)

#put in the information
#entered a raw number here, as a reminder
tableprint[1 , ] = c("Non-Random Intercept", temp$AIC, temp$BIC,
                     temp$logLik, 30409, "-", "-")

temp = summary(model3)
tableprint[2 , ] = c("Random Intercept", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms, r.squaredGLMM(model3))

temp = summary(model4.1)
tableprint[3 , ] = c("Harm High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.1))

temp = summary(model4.2)
tableprint[4 , ] = c("Harm Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.2))

temp = summary(model4.3)
tableprint[5 , ] = c("Fairness High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.3))

temp = summary(model4.4)
tableprint[6 , ] = c("Fairness Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.4))

temp = summary(model4.5)
tableprint[7 , ] = c("Ingroup High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.5))

temp = summary(model4.6)
tableprint[8 , ] = c("Ingroup Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.6))

temp = summary(model4.7)
tableprint[9 , ] = c("Authority High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.7))

temp = summary(model4.8)
tableprint[10 , ] = c("Authority Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.8))

temp = summary(model4.9)
tableprint[11 , ] = c("Purity High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.9))

temp = summary(model4.10)
tableprint[12 , ] = c("Purity Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.10))
#keep going

#round and clean up
tableprint[ , 2:4] = printnum(as.numeric(tableprint[ , 2:4]))
tableprint[-1 , 6] = printp(as.numeric(tableprint[-1 , 6]))
tableprint[-1 , 7] = printp(as.numeric(tableprint[-1 , 7]))

apa_table.latex(as.data.frame(tableprint),
          align = c("l", rep("c", 6)), 
          caption = "MLM Model Statistics",
          note = "Degrees of freedom indicate residual $df$ for each model.",
          escape = FALSE
 )
```

To analyze if news sources adhered to differences in word use based on their target audience, we utilized a multilevel model (MLM) to analyze the data. MLM is a regression technique that allows one to control for the repeated measurement and nest structured of the data, which creates correlated error [@CITE_gelman]. First, an intercept only model was created using percent text overall as the dependent variable. Using the *nlme* library in *R* [@CITE_nlme], a model with the news source as the random intercept was analyzed to determine if it was necessary to control for correlated error. Table @\ref(tab:model-table) includes the model statistics for all models. While the $\Delta\chi^2$(1) = `r printnum(anova(model1,model3)[,8][2]))`, *p* = `r printp(anova(model1,model3)[,9][2])` was not significant, all models were still structured with a random intercept by source to control for even a small amount of correlated error.

Next, predictor models with political lean predicting percent of MFD words was analyzed for each of the MFD categories separately (i.e., "harm-positive", "harm-negative", etc.). Coefficient values indicate the mean differences between conservative and liberal sources, and to help illustrate these differences, the overall means were plotted in Figure \@ref(fig:graph-means). For harm words, there was not a significant difference in the words indicating harm-negative *b* = `r printnum(summary(model4.1)$tTable[2,1])`, *t*(`r summary(model4.1)$tTable[2,3]`) = `r printnum(summary(model4.1)$tTable[2,4])`, *p* = `r printp(summary(model4.1)$tTable[2,5])` or harm-positive *b* = `r printnum(summary(model4.2)$tTable[2,1])`, *t*(`r summary(model4.2)$tTable[2,3]`) = `r printnum(summary(model4.2)$tTable[2,4])`, *p* = `r printp(summary(model4.2)$tTable[2,5])`.

```{r graph-means, echo=FALSE}
#make a ggplot here! :) 
#put the categories on the bottom X
#put the lean as the group
#y is the percent
#use the long_mlm dataset
#i will make low and high happen as different panels

@@

# Discussion
How it turned out
